Energy spectrum of diatomic molecules\\ in the Quantum Drude Oscillator model

### 2022-06-27 paper/main.tex
tables added

    Performing the following change of variable:
    \begin{equation}
        \psi_+(x)=\exp\left[\frac{\gamma^2-4\beta\delta}{8k\delta^{3/2}}\,x-\frac{\gamma}{4k\delta^{1/2}}\,x^2-\frac{\delta^{1/2}}{3k}\,x^3\right]\phi_+(x)
    \end{equation}
    we obtain:
    \begin{widetext}
    \begin{equation}
    \begin{split}
        &\frac{\text{d}^2\phi_+}{\text{d}x^2}(x)+\left[\frac{\gamma^2-4\beta\delta}{4k\delta^{3/2}}-\frac{\gamma}{k\delta^{1/2}}\,x-\frac{2\delta^{1/2}}{k}\,x^2\right]\frac{\text{d}\phi_+}{\text{d}x}(x)\\
        &+\left[\frac{16 \delta ^2 \left(\beta ^2+4 \delta  \epsilon \right)-8 \beta  \gamma ^2 \delta +\gamma ^4-32 \gamma  \delta ^{5/2} k}{64 \delta ^3 k^2}-\frac{8 \alpha  \delta ^2-4 \beta  \gamma  \delta +\gamma ^3+16 \delta ^{5/2} k}{8 \delta ^2 k^2}\,x\right]\phi_+(x)=0\,,
    \end{split}
    \end{equation}
    \end{widetext}
    which is known as the so-called \textit{tri-confluent Heun equation}.
    We further perform the following change of variable, the reason why to become clear soon:
    \begin{equation}
        \phi_+(x)=(1+x)^{\frac{4 \beta  \gamma  \delta -\gamma ^3-8 \delta ^2 \left(\alpha +2k \delta^{1/2} \right)}{16k \delta ^{5/2}}}f_+(x)\,,
    \end{equation}
    as well as map the positive real axis to the segment $[0,1]$ through the change of argument
    \begin{equation}
        z=\frac{x}{x+1}\,,
    \end{equation}
    and look for a solution of the obtained ODE in terms of a series expansion at zero of the form:
    \begin{equation}
        f_+(z)=\sum_{n\geq 0}c^+_nz^n\,.
    \end{equation}
    Plugging the ansatz into the differential equation, we obtain the following recurrence relation between the coefficients:
    \begin{widetext}
    \begin{equation}
    \begin{split}
        &(n+1)(n+2) c^+_{n+2}+(n+1)(A -4n)c^+_{n+1} +[6(n-1) n+B n+E]c^+_n \\
        &+[C (n-1)+F-4(n-2) (n-1)]c^+_{n-1} + [(n-3) (n-2)+D (n-2)+G]c^+_{n-2}=0\ \ \ (n\geq 2)
    \end{split}
    \end{equation}
    \end{widetext}
    where the various coefficients are listed in full details in appendix. The coefficients $c^+_0$ and $c^+_1$ are to be fixed through boundary conditions, and the coeffients $c^+_2$ and $c^+_3$ are in turn fixed by the following relations
    \begin{equation}
    \begin{split}
        c^+_2&=-Ec^+_0-Ac^+_1\,,\\
        c^+_3&=-\frac{ F c^+_0+(B+E)c^+_1 +2 (A-4)c^+_2 }{6}\,.
    \end{split}
    \end{equation}
    Let us similarly denote by $c^-_n$ the coefficients in the series expansion corresponding to the solution on the negative real axis. It has been shown in \cite{Lay_1998} and \cite{doi:10.1063/1.531962} that the smooth matching of the two solutions at the origin can be achieved by imposing the so-called \textit{dominant solution} to the above defined difference equations vanishes. The conditions
    \begin{equation}
        \psi_+(0) = \psi_-(0)\ \ \ \text{and}\ \ \ \frac{\text{d}\psi_+}{\text{d}x}(0) = \frac{\text{d}\psi_-}{\text{d}x}(0)
    \end{equation}
    lead to constraints on the initial conditions for the difference equations, namely that $c^+_0 = c^-_0$ and:
    \begin{equation}
    \label{eq:initial_constraint}
    \begin{split}
        &c^+_1-c^+_0 \left[1+\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (\gamma+2 \beta )+\gamma ^3}{16 \delta ^{5/2} k}\right]\\
        & = -c^-_1+c^-_0 \left[1-\frac{8 \delta ^2 (\alpha -\beta )+2 \gamma  \delta  (\gamma -2 \beta )+\gamma ^3}{16 \delta ^{5/2} k}\right]
    \end{split}
    \end{equation}
    The two sides of relation (\ref{eq:initial_constraint}) are therefore equal to some quantity $s$, which parameterizes the solution. Now, the vanishing of the dominant solution can be achieved by imposing that the series coefficients $c^+_n(\epsilon, s)$ and $c^-_n(\epsilon, s)$ are identically $0$ asymptotically in $n$. This provides a pair of algebraic equations in the energy variable $\epsilon$ and the \textit{shift} variable $s$.

@@

\begin{table}[h!]
\caption{\label{tab:table1} Ground state energy (in Ha) of the H-H system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0\\
    \hline
    1.0 & 5.428021 & 1.000000 & 3.673658 \\
    2.0 & 0.531071 & 0.210137 & 0.872826 \\
    3.0 & 1.532129 & 0.957917 & 0.999836 \\
    4.0 & 1.968642 & 0.999963 & 1.000023 \\
    5.0 & 0.031075 & 1.000000 & 1.014180 \\
    6.0 & 0.978062 & 5.375749 & 0.970292 \\
    7.0 & 21.654276 & 0.558010 & -34.785660 \\
    8.0 & 43.488829 & 85.452632 & -28.868817
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}[h!]
\caption{\label{tab:table2} Ground state energy (in Ha) of the He-He system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0\\
    \hline
    1.0 & 1.000000 & 1.000000 & 5.739538 \\
    2.0 & 1.266281 & 1.134311 & -0.966946 \\
    3.0 & 0.880808 & 0.147328 & -0.206244 \\
    4.0 & 3.755382 & 0.136923 & 1.000000 \\
    5.0 & 1.000000 & 0.999847 & 0.415453 \\
    6.0 & 6.604936 & 1.000000 & -1.709232 \\
    7.0 & 1.000008 & 1.000000 & 9.223832 \\
    8.0& 198.102785 & 1.000000 & 20.246740
\end{tabular}
\end{ruledtabular}
\end{table}

    \begin{figure}[h!]
        \centering
            \includegraphics[scale=0.33]{plus_minus_coefs}
            \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$.}
    \end{figure}

@@

    \begin{widetext}
    \begin{equation*}
    \begin{split}
        &A=-\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (2 \beta +\gamma )+\gamma ^3+32 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        &B=\frac{8 \delta ^2 (3 \alpha +2 \beta -\gamma )-4 \gamma  \delta  (3 \beta +\gamma )+3 \gamma ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        &C=-\frac{8 \delta ^2 (3 \alpha +\beta -\gamma )-2 \gamma  \delta  (6 \beta +\gamma )+3 \gamma ^3+16 \delta ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        &D=\frac{-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)}{8 \delta ^{5/2} k}\\
        &E=\frac{4 \gamma ^2 \delta ^2 \left(\gamma  (4 \alpha +\gamma )+4 \beta ^2+8 \beta  \gamma \right)-32 \gamma  \delta ^3 (\alpha +\beta ) (2 \beta +\gamma )+64 \delta ^4 (\alpha +\beta )^2-4 \gamma ^4 \delta  (2 \beta +\gamma )+\gamma ^6+256 \delta ^5 \left(2 k^2+\epsilon \right)+128 \delta ^{9/2} k (3 \alpha +2 \beta -\gamma )-64 \gamma  \delta ^{7/2} k (3 \beta +\gamma )+48 \gamma ^3 \delta ^{5/2} k}{256 \delta ^5 k^2}\\
        &F=-\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \gamma  \delta  (\beta +2 \delta )+\gamma ^3-2 \gamma ^2 \delta +8 \delta ^2 \left(\alpha +\beta +2 \delta +4 \sqrt{\delta } k\right)\right)}{128 \delta ^5 k^2}\\
        &G=\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)\right)}{256 \delta ^5 k^2}
    \end{split}
    \end{equation*}
    \end{widetext}

>>>>

    Performing the following change of variable:
    \begin{equation}
        \psi_+(x)=\exp\left[\frac{\gamma^2-4\beta\delta}{8k\delta^{3/2}}\,x-\frac{\gamma}{4k\delta^{1/2}}\,x^2-\frac{\delta^{1/2}}{3k}\,x^3\right]\phi_+(x)
    \end{equation}
    we obtain:
    \begin{widetext}
    \begin{equation}
    \begin{split}
        &\frac{\text{d}^2\phi_+}{\text{d}x^2}(x)+\left[\frac{\gamma^2-4\beta\delta}{4k\delta^{3/2}}-\frac{\gamma}{k\delta^{1/2}}\,x-\frac{2\delta^{1/2}}{k}\,x^2\right]\frac{\text{d}\phi_+}{\text{d}x}(x)\\
        &+\left[\frac{16 \delta ^2 \left(\beta ^2+4 \delta  \epsilon \right)-8 \beta  \gamma ^2 \delta +\gamma ^4-32 \gamma  \delta ^{5/2} k}{64 \delta ^3 k^2}-\frac{8 \alpha  \delta ^2-4 \beta  \gamma  \delta +\gamma ^3+16 \delta ^{5/2} k}{8 \delta ^2 k^2}\,x\right]\phi_+(x)=0\,,
    \end{split}
    \end{equation}
    \end{widetext}
    which is known as the so-called \textit{tri-confluent Heun equation}.
    We further perform the following change of variable, the reason why to become clear soon:
    \begin{equation}
    \label{eq:change_variable}
        \phi_+(x)=(1+x)^{\frac{4 \beta  \gamma  \delta -\gamma ^3-8 \delta ^2 \left(\alpha +2k \delta^{1/2} \right)}{16k \delta ^{5/2}}}f_+(x)\,,
    \end{equation}
    as well as map the positive real axis to the segment $[0,1]$ through the change of argument
    \begin{equation}
        z=\frac{x}{x+1}\,,
    \end{equation}
    and look for a solution of the obtained ODE in terms of a series expansion at zero of the form:
    \begin{equation}
        f_+(z)=\sum_{n\geq 0}c^+_nz^n\,.
    \end{equation}
    Plugging the ansatz into the differential equation, we obtain the following recurrence relation between the coefficients:
    \begin{widetext}
    \begin{equation}
    \begin{split}
        &(n+1)(n+2) c^+_{n+2}+(n+1)(A -4n)c^+_{n+1} +[6(n-1) n+B n+E]c^+_n \\
        &+[C (n-1)+F-4(n-2) (n-1)]c^+_{n-1} + [(n-3) (n-2)+D (n-2)+G]c^+_{n-2}=0\ \ \ (n\geq 2)
    \end{split}
    \end{equation}
    \end{widetext}
    where the various coefficients are listed in full details in appendix. The change of variable (\ref{eq:change_variable}) is chosen precisely such that the order of the above difference equation is as small as possible. The coefficients $c^+_0$ and $c^+_1$ are to be fixed through boundary conditions, and the coeffients $c^+_2$ and $c^+_3$ are in turn fixed by the following relations
    \begin{equation}
    \begin{split}
        c^+_2&=-Ec^+_0-Ac^+_1\,,\\
        c^+_3&=-\frac{ F c^+_0+(B+E)c^+_1 +2 (A-4)c^+_2 }{6}\,.
    \end{split}
    \end{equation}
    Let us similarly denote by $c^-_n$ the coefficients in the series expansion corresponding to the solution on the negative real axis. It has been shown in \cite{Lay_1998} and \cite{doi:10.1063/1.531962} that the smooth matching of the two solutions at the origin can be achieved by imposing the so-called \textit{dominant solution} to the above defined difference equations vanishes. The conditions
    \begin{equation}
        \psi_+(0) = \psi_-(0)\ \ \ \text{and}\ \ \ \frac{\text{d}\psi_+}{\text{d}x}(0) = \frac{\text{d}\psi_-}{\text{d}x}(0)
    \end{equation}
    lead to constraints on the initial conditions for the difference equations, namely that $c^+_0 = c^-_0$ and:
    \begin{equation}
    \label{eq:initial_constraint}
    \begin{split}
        &c^+_1-c^+_0 \left[1+\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (\gamma+2 \beta )+\gamma ^3}{16 \delta ^{5/2} k}\right]\\
        & = -c^-_1+c^-_0 \left[1-\frac{8 \delta ^2 (\alpha -\beta )+2 \gamma  \delta  (\gamma -2 \beta )+\gamma ^3}{16 \delta ^{5/2} k}\right]
    \end{split}
    \end{equation}
    The two sides of relation (\ref{eq:initial_constraint}) are therefore equal to some quantity $s$, which parameterizes the solution. Now, the vanishing of the dominant solution can be achieved by imposing that the series coefficients $c^+_n(\epsilon, s)$ and $c^-_n(\epsilon, s)$ are identically $0$ asymptotically in $n$. This provides a pair of algebraic equations in the energy variable $\epsilon$ and the \textit{shift} variable $s$.

@@

    \begin{table}[h!]
    \caption{\label{tab:Ar-Ar} Energy spectrum (in Ha) of the Ar-Ar system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 9.247342 & 32.416619 & 62.971511 \\
        1.0 & 2.981229 & 10.350087 & 20.248422 \\
        1.5 & 1.563464 & 5.442288 & 10.069702 \\
        2.0 & 1.023301 & 3.394336 & 6.337199 \\
        2.5 & 0.748161 & 2.413177 & 4.876881 \\
        3.0 & 0.590991 & 1.960271 & 4.289340 \\  
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Cs-Cs} Energy spectrum (in Ha) of the Cs-Cs system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 4.076335 & 14.287104 & 27.755741 \\
        1.0 & 1.307214 & 4.543529 & 8.897871 \\
        1.5 & 0.673427 & 2.362932 & 4.396492 \\
        2.0 & 0.426306 & 1.441411 & 2.686432 \\
        2.5 & 0.296956 & 0.971662 & 1.957474 \\
        3.0 & 0.217699 & 0.719613 & 1.585340 \\    
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:H-H} Energy spectrum (in Ha) of the H-H system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 3.757546 & 13.234211 & 25.693826 \\
        1.0 & 1.213930 & 4.243743 & 8.293979 \\
        1.5 & 0.649664 & 2.239448 & 4.116225 \\
        2.0 & 0.436524 & 1.423565 & 2.744604 \\
        2.5 & 0.330635 & 1.081656 & 2.284054 \\
        3.0 & 0.279296 & 0.965099 & 2.204208 \\      
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:He-He} Energy spectrum (in Ha) of the He-He system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 4.838555 & 16.998352 & 32.990230 \\
        1.0 & 1.609674 & 5.563162 & 10.796479 \\
        1.5 & 0.928052 & 3.096340 & 5.617631 \\
        2.0 & 0.690066 & 2.190579 & 4.209331 \\
        2.5 & 0.597424 & 1.987363 & 4.173586 \\
        3.0 & 0.607965 & 2.159394 & 4.851867 \\       
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:K-K} Energy spectrum (in Ha) of the K-K system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 3.900846 & 13.629450 & 26.449767 \\
        1.0 & 1.254074 & 4.338725 & 8.463017 \\
        1.5 & 0.646062 & 2.260433 & 4.233126 \\
        2.0 & 0.409452 & 1.389547 & 2.556108 \\
        2.5 & 0.286775 & 0.935829 & 1.841376 \\
        3.0 & 0.211508 & 0.689674 & 1.476942 \\         
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Kr-Kr} Energy spectrum (in Ha) of the Kr-Kr system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 9.936548 & 34.839598 & 67.682787 \\
        1.0 & 3.196890 & 11.107797 & 21.743625 \\
        1.5 & 1.666467 & 5.817323 & 10.779216 \\
        2.0 & 1.078692 & 3.598874 & 6.723190 \\
        2.5 & 0.776461 & 2.514230 & 5.085759 \\
        3.0 & 0.599348 & 1.984794 & 4.360291 \\           
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Li-Li} Energy spectrum (in Ha) of the Li-Li system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 2.989579 & 10.393189 & 20.094511 \\
        1.0 & 0.965106 & 3.317199 & 6.411919 \\
        1.5 & 0.498061 & 1.728672 & 3.276409 \\
        2.0 & 0.316132 & 1.076633 & 1.951989 \\
        2.5 & 0.223280 & 0.727240 & 1.384589 \\
        3.0 & 0.166518 & 0.533844 & 1.098635 \\              
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Ne-Ne} Energy spectrum (in Ha) of the Ne-Ne system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 8.067324 & 28.257747 & 54.866835 \\
        1.0 & 2.648128 & 9.141505 & 17.802546 \\
        1.5 & 1.463214 & 4.975572 & 9.086247 \\
        2.0 & 1.037985 & 3.321372 & 6.216936 \\
        2.5 & 0.839105 & 2.707087 & 5.494303 \\
        3.0 & 0.769833 & 2.636825 & 5.742950 \\             
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Rb-Rb} Energy spectrum (in Ha) of the Rb-Rb system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 4.031874 & 14.113400 & 27.409612 \\
        1.0 & 1.294297 & 4.489885 & 8.780383 \\
        1.5 & 0.666759 & 2.337266 & 4.359340 \\
        2.0 & 0.422361 & 1.430245 & 2.650383 \\
        2.5 & 0.294937 & 0.963709 & 1.922279 \\
        3.0 & 0.216807 & 0.712417 & 1.550805 \\                
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{table}[h!]
    \caption{\label{tab:Xe-Xe} Energy spectrum (in Ha) of the Xe-Xe system}
    \begin{ruledtabular}
    \begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
        \hline
        0.5 & 10.472412 & 36.762340 & 71.427248 \\
        1.0 & 3.360994 & 11.705550 & 22.941485 \\
        1.5 & 1.743863 & 6.103626 & 11.305873 \\
        2.0 & 1.117696 & 3.742926 & 7.034869 \\
        2.5 & 0.792188 & 2.580753 & 5.270133 \\
        3.0 & 0.598300 & 1.992258 & 4.438638 \\                 
    \end{tabular}
    \end{ruledtabular}
    \end{table}

    \begin{figure}[h!]
        \centering
            \includegraphics[scale=0.33]{plus_minus_coefs}
            \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$. The purple dots correspond to the first excited states of the H-H system for $r=4$ and $\mathcal E=0$.}
    \end{figure}

@@

    \begin{widetext}
    \begin{equation*}
    \begin{split}
        A&=-\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (2 \beta +\gamma )+\gamma ^3+32 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        B&= \frac{8 \delta ^2 (3 \alpha +2 \beta -\gamma )-4 \gamma  \delta  (3 \beta +\gamma )+3 \gamma ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        C&= -\frac{8 \delta ^2 (3 \alpha +\beta -\gamma )-2 \gamma  \delta  (6 \beta +\gamma )+3 \gamma ^3+16 \delta ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        D&= \frac{-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)}{8 \delta ^{5/2} k}\\
        E&= \frac{4 \gamma ^2 \delta ^2 \left(\gamma  (4 \alpha +\gamma )+4 \beta ^2+8 \beta  \gamma \right)-32 \gamma  \delta ^3 (\alpha +\beta ) (2 \beta +\gamma )+64 \delta ^4 (\alpha +\beta )^2-4 \gamma ^4 \delta  (2 \beta +\gamma )}{256 \delta ^5 k^2}\\
       &\ \ \ \ \ \  +\frac{\gamma ^6+256 \delta ^5 \left(2 k^2+\epsilon \right)+128 \delta ^{9/2} k (3 \alpha +2 \beta -\gamma )-64 \gamma  \delta ^{7/2} k (3 \beta +\gamma )+48 \gamma ^3 \delta ^{5/2} k}{256 \delta ^5 k^2}\\
        F&= -\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \gamma  \delta  (\beta +2 \delta )+\gamma ^3-2 \gamma ^2 \delta +8 \delta ^2 \left(\alpha +\beta +2 \delta +4 \sqrt{\delta } k\right)\right)}{128 \delta ^5 k^2}\\
        G&= \frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)\right)}{256 \delta ^5 k^2}
    \end{split}
    \end{equation*}
    \end{widetext}
